---
title: "Activity 3 - MLR"
auhor: "Banabas Kariuki"
output: github_document
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Day 1

## Load the necessary packages

```{r, message=FALSE}
library(tidyverse)
library(tidymodels)
library(GGally)
```

## Load the data

```{r}
hfi <- read_csv("~/Preparations/STA 631/activity03-mlr/day01-quantitative-explanatory/hfi.csv")
head(hfi)
```

#Fltering the 2016 Data and creating a dataframe
```{r}
hfi_2016 <- data.frame(filter(hfi, year == 2016))
#or
#hfi_2016<- hfi %>% filter(year == 2016)
#hfi_2016 <- data_frame(hfi_2016)
head(hfi_2016)
```

##Pairs Plot

```{r pairs-plot}
hfi_2016 %>% select(pf_score, pf_expression_control, pf_association) %>% ggpairs()
```


1. For each pair of variables, how would you describe the relationship graphically?
  Do any of the relationships look linear?
  Are there any interesting/odd features (outliers, non-linear patterns, etc.)?

2. For each pair of variables, how would you describe the relationship numerically?


3. Are your two explanatory variables collinear (correlated)?
  Essentially, this means that adding more than one of these variables to the model would not add much value to the model.
  We will talk more on this issue in Activity 4 (other considerations in regression models).


## The multiple linear regression model

```{r mrl-model}
#fit the mlr model
lm_spec<- linear_reg() %>% set_mode("regression") %>% set_engine("lm")
lm_spec

mlr_mod<- lm_spec %>% fit(pf_score ~ pf_expression_control + pf_association, data = hfi_2016)

#model output
tidy(mlr_mod)
```



